%-------------------------
% Resume in Latex
% Author : Maluki Muthusi
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
    \item\small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}        \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\skillListStart}{\begin{description}[leftmargin=*,noitemsep]}
\newcommand{\skillListEnd}{\end{description}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{\href{https://maluki.sharehen.com}{\Large Maluki Muthusi}} & Email : \href{mailto:malukimuthusi@gmail.com}{malukimuthusi@gmail.com}\\
    Website: \href{https://maluki.sharehen.com}{maluki.sharehen.com} & Mobile : +254790497466\\
    LinkedIn: \href{https://www.linkedin.com/in/maluki-muthusi}{maluki-muthusi} & Twitter \href{https://twitter.com/MalukiMuthusi}{@MalukiMuthusi}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Software Engineering Experience}

\resumeSubHeadingListStart

%% software engineer savannah informatics
\resumeSubheading{Savannah Informatics}{Nairobi, Kenya}{Software Engineer}{Feb 2021 -- June 2021}

\resumeItemListStart
\resumeItem{Microservices}{Design Microservices for the health cloud application.}

\resumeItem{Flutter App Archicture}{Develop the architecture of Be.Well cross platform mobile app}

\resumeItem{Graphql}{Serve APIs through graphql API server}

\resumeItemListEnd

%% backend developer savannah informatics
\resumeSubheading{Savannah Informatics}{Nairobi, Kenya}{Backend Developer}{August 2020 -- January 2021}

\resumeItemListStart
\resumeItem{Tests}{Increase code coverage from 0 to 95\%. Test the business logic}

\resumeItem{Code Deployment}{Automate Code Deployment using Docker}
\resumeItemListEnd

%% Network training
\resumeSubheading{Network Trainee}{ICT Centre UON}{Network Trainee}{June 2019 -- September 2019}

\resumeItemListStart
\item Configuring routers, switches, APs, and firewalls
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education and Certifications-----------------
\section{Education and Certifications}

\resumeSubHeadingListStart

\resumeSubheading{University of Nairobi}{Nairobi, Kenya}{Bachelor of Science in Computer Science }{May 2021}

\resumeSubheading{The Linux Foundation}{Online}{\href{https://www.credly.com/badges/ab918a14-4dfd-4800-be45-a6a3a8fbd96c/linked_in}{JSNAD: OpenJS Node.js Application Developer}}{June 2021}

\resumeSubheading{Huawei Certifications}{ICT Centre UON}{HCIA Network Security }{January 2020}

\resumeSubheading{Huawei Certifications}{ICT Centre UON}{HCIA Routing and Switching  }{July 2019}

\resumeSubheading{HarvardX}{Online}{Crossroads: Entrepreneurship in Emerging Economies  }{January 2020}

\resumeSubHeadingListEnd

%-----------Technical Skills-----------------
\section{Technical Skills}

\skillListStart

\item[Languages: ] Go, Dart, Kotlin, C, Java, Python, JavaScript

\item[Frameworks: ] Android, GraphQL, Django

\item[Databases]            MongoDB,PostgreSQL, MySQL, Firestore

\item [Platforms and tools:] Flutter, Node.js, Linux, Google Cloud Platform, Firebase, Gitlab CI/CD, Github, git, \LaTeX, Docker, Kubernetes

\skillListEnd


%-----------Technical Skills-----------------
\section{Awards And Achievements}

\begin{itemize}[noitemsep]
    \item Lead a team to winning Global ICT Competition 2019/2020. The competition is based on practical skills on computer networks and security.
    \item Won National ICT Competition 2019/2020. I was the top student in Kenya. The competition involves hands on skills assessment in network configuration and security. Topics include TCP/IP protocols, routing protocols, and securing networks. \href{https://www.uonbi.ac.ke/news/uon-student-wins-huawei-network-cloud-track-award}{Link to the awards article}
\end{itemize}

%-----------Roles-----------------
\section{Roles}
\begin{itemize}[noitemsep]
    \item Lead Developer Students Club (DSC) at University of Nairobi. Key role is bridging the gap between theory and practical skills.
    \item Lead Huawei Campus Ambassador. Key role is to assist students to gain practical skills through certifications from Huawei University of Nairobi Campus.
\end{itemize}


%-------------------------------------------
\end{document}